---
title: "Dataset Generator"
output: html_document
date: "2023-10-20"
---
# After-cleanning Dataset generator
Description:
This is a Rmd for dataset generation, which will write out cleanned dataset or sampled dataset as per our's analysis need.

This files is based on the insight we derived from the EDA file, the work flow is: EDA -> Data Cleanning -> Data Analysis.

## Download Necessary Packages
```{r setup, include=FALSE}
# List of packages to install
packages_to_install <- c("tidyverse", "data.table", "ggplot2", "RPostgreSQL")

# Loop through the list of packages and install them if not already installed
for (package in packages_to_install) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package)
  }
}
```

## Improt necessary packages
```{r, include = False}
library(data.table)
library(tidyverse)
library(ggplot2)
# link to the data base
library(RPostgreSQL)
```


## Read datasets, 4 smaller dataset
```{r}
df_depinfo = fread("deptinfo.csv")
df_sksinfo = fread("skstinfo.csv")
df_skuinfo = fread("skuinfo.csv")
df_strinfo = fread("strinfo.csv")
```

Note there 's a column of NULL, remove it
```{r}
df_skuinfo_2 = df_skuinfo |>
  select(-V11)
```

### Consider remove rows:
```{r}
# Remove redundant/breaking/missing rows
# TBD
```


### The sampling function:
```{r}
SampledDataset = function(dataset, sample_size = 100, file_path, seed = 400) {
  if (!is.null(seed)) {
    set.seed(seed)  # Set the seed if provided
  }
  # Randomly sample rows
  sampled_data <- data %>% sample_n(sample_size)
  
  # Write the sampled data to a CSV file
  write.csv(sampled_data, file = file_path, row.names = FALSE)
  
  return(file_path)
}

# Check the file path where the CSV file was saved:
# cat("CSV file saved at:", file_path, "\n")
```

## Read trnsact.txt, the largest dataset
### Use SQL for Efficiency Query
```{r}
# Define the connection parameters
db_connection <- dbConnect(
  PostgreSQL(),
  user = "jialong7",
  password = "password",
  host = "pg.analytics.northwestern.edu",
  port = 5432,
  dbname = "everything2023"
)
```

```{r}
# column 9 and 10 are exactly the same, column 13 is binary without clear meaning, so drop column 10 and 13.
# while right now I don't know why col 13 is binary, so just stop doing this.
query <- "SELECT * FROM group_6.\"TRNSACT\""

# Use dbGetQuery to fetch the result
result <- dbGetQuery(db_connection, query)

# Print the result
cat("OUTPUT: ", result$count, "\n")
```

